M-M paper, morphological bias

### 2015-03-24 papers/MbhMsph/mm.tex
tue

here: 66 galaxies, largest dataset to date
status-of-the-art decomp.
3.6 um best tracer of stellar mass
9 systems w $M_{\rm BH} \lesssim 10^7\rm~M_\odot$
17 spirals

\section{Data}
\label{sec:data}

>>>>

Here we investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
using state-of-the-art galaxy decompositions (Savorgnan \& Graham \emph{in preparation}, hereafter \emph{Paper I}) 
for the largest sample of galaxies with directly measured black hole masses.
Our decompositions were obtained from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
which is an excellent proxy for the stellar mass, superior to the $K-$band (\citealt{sheth2010} and references therein).
Nine of our galaxies have $M_{\rm BH} \lesssim 10^7\rm~M_\odot$, 
which allows us to accurately constrain the slope of the correlation at the low-mass end.
In addition to this, our galaxy sample includes 17 spiral galaxies, 
representing a notable improvement over the past studies dominated by early-type systems.

\section{Data}
\label{sec:data}
Our galaxy sample consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Our state-of-the-art galaxy decompositions take into account 
bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
We have additionally used kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} 
to confirm the presence of rotationally supported components in most early-type galaxies, 
and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
Details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
together with the individual 66 galaxy decompositions, will be presented in \emph{Paper I}.
